\documentclass{article}
\usepackage{tikz}
\usepackage{verbatim}
\usetikzlibrary{arrows,shapes}

\usepackage{wine}

\begin{document}
\title{\LaTeX{} Wine Stains}
\author{LianTze Lim}
\renewcommand{\today}{24 February 2016}
\maketitle

\wineAm{1}{1.0}{0}{5.5cm}{3cm}
 
\section{Introduction}
Now you can add wine stains to your \LaTeX{} documents, too! \texttt{wine.sty} is really Hanno Rein's \texttt{coffee4.sty}\footnote{http://hanno-rein.de}, with all the `\texttt{coffee}' replaced by `\texttt{wine}' in the code, and replaced colour definitions.

You can choose from four different stain types:
\begin{enumerate}
  \item $270^\circ$ circle stain with two tiny splashes 
  \item $60^\circ$ circle stain 
  \item two splashes with light colours
  \item and a colourful twin splash.
\end{enumerate}

\section{Usage}
To use the package, simply place the \texttt{wine.sty} file in the directory with all of your 
other \texttt{.tex} files. 
Then include the following line in the header of your document:
\begin{verbatim}
\usepackage{wine}
\end{verbatim}
To place a wine stain on a page, put one of the following commands in the source code of the relevant page: 
\begin{verbatim}
\wineAm{alpha}{scale}{angle}{xoff}{yoff}
\wineBm{alpha}{scale}{angle}{xoff}{yoff}
\wineCm{alpha}{scale}{angle}{xoff}{yoff}
\wineDm{alpha}{scale}{angle}{xoff}{yoff}
\end{verbatim}
where alpha is the transparency factor $\in [0,1]$. The scale factor is {\tt scale}, and the standard is {\tt scale}=1. 
The angle is in degrees $\in [0,360]$. 
The position relative to the centre of the page is given by x and y offs \texttt{xoff} and \texttt{yoff}.

\section{Copyright}
\emph{(The following is Hanno Rein's copyright statement:}

You can freely distribute this package as I do not believe in imaginary property. All stains are self-made, photographed by myself, processed with gimp and traced with Inkscape.
Donations should be made in coffee only. My address is
\begin{quote}
Hanno Rein\\
DAMTP, CMS\\
Wilberforce Road\\
Cambridge CB3 0WA\\
United Kingdom
\end{quote}
See more wine stains on the next pages.
\wineCm{0.9}{1}{180}{0}{0}
\newpage
\wineDm{0.4}{0.5}{90}{0}{0}
\newpage
\wineBm{0.7}{1}{0}{0}{0}

\newpage
\wineAm{0.7}{0.75}{2}{0}{0}

\end{document}
